Planetary perturbers: Flaring star-planet interactions in Kepler and TESS

### 2023-10-09 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{table*}
\script{paper_main_table.py}
\movetableright=-20mm

    \caption{Flaring single star-planet system parameters.}
\scriptsize
    \input{output/table_lit_vals.tex}
        \label{tab:maintable_lit}
    \tablerefs{\input{output/lit_table_bibstring.tex}}
\end{table*}

@@

\begin{figure}[ht!]
    \script{paper_lx_plots.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_lxlbol.png}
        \caption{
           X-ray luminosity over bolometric luminosity compared to Rossby number (\textbf{upper panel}), and average surface magnetic field strength (\textbf{lower panel}). Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3082, which is underluminous for its Rossby number, and hence also its estimated magnetic field appears too strong for its $L_X/L_{\rm bol}$.
        }
        \label{fig:lx}
    \end{centering}
\end{figure}

@@

\begin{figure*}[ht!]
    \script{paper_adtest_vs_value_scatterplots.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_bg_main.png}
        \caption{
            Expected power of magnetic SPI vs. AD test results, assuming the stretch-and-break scenario with an unmagnetized planet. While no individual system amounts to a $>3\sigma$ detection, the global trend is intriguing: Systems with low expected power show no deviation from random intrinsic flaring (i.e. high $p$-values). In contrast, systems with high expected power show two branches. One where the significance of interaction increases with power, and one without such a trend. See Fig.~\ref{fig:adtest_ro} in the Appendix for the same figure, color-coded by Rossby number.
        }
        \label{fig:adtest_bp}
    \end{centering}
\end{figure*}

>>>>

\begin{longrotatetable}
\script{paper_main_table.py}
\movetableright=-20mm
    % \caption{Flaring single star-planet system parameters. Obs. time is the total observing time with Kepler and TESS.}
% \footnotesize
    \input{output/table_lit_vals.tex}
        \label{tab:maintable_lit}
    \tablerefs{\input{output/lit_table_bibstring.tex}}
\end{longrotatetable}

@@

\begin{figure}[ht!]
    \script{paper_lx_plots.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_lxlbol.png}
        \caption{
           X-ray luminosity over bolometric luminosity compared to Rossby number (\textbf{upper panel}), and average surface magnetic field strength (\textbf{lower panel}). \textcolor{red}{Blue lines denote the error bars, grey lines point to the IDs of the corresponding stars.} Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3082, which is underluminous for its Rossby number, and hence also its estimated magnetic field appears too strong for its $L_X/L_{\rm bol}$.
        }
        \label{fig:lx}
    \end{centering}
\end{figure}

@@

\begin{figure*}[ht!]
    \script{paper_adtest_vs_value_scatterplots.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_bg_main.png}
        \caption{
            Expected power of magnetic SPI vs. AD test results, assuming the stretch-and-break scenario with an unmagnetized planet. \textcolor{red}{The vertical and horizontal grey lines denote the uncertainties quoted in Table~\ref{tab:maintable_der}.} While no individual system amounts to a $>3\sigma$ detection, the global trend is intriguing: Systems with low expected power show no deviation from random intrinsic flaring (i.e. high $p$-values). In contrast, systems with high expected power show two branches. One where the significance of interaction increases with power, and one without such a trend. See Fig.~\ref{fig:adtest_ro} in the Appendix for the same figure, color-coded by Rossby number.
        }
        \label{fig:adtest_bp}
    \end{centering}
\end{figure*}
